### 2024-01-15 documentation/thesis/thesis_document.tex
more thesis
first: all chapters filles :)

The following section defines some usecases that the future project
should be able to cover. These illustrate practical situations to
understand the functionality and added value of the implemented solution
for the user. These were defined in the course of project planning and
provide an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{evaluation}, the defined usecases are also used as a
reference to demonstrate the implemented capabilities of the solution.

@@

A defined main objective of this project is the development of a
cost-effective magnetic field sensors interface that is also universally
expandable. The focus is on mapping different sensors and being
compatible with different magnet types and shapes. This ensures broad
applicability in different scenarios. Another goal is reproducibility to
ensure consistent results. Easy communication with standard PC hardware
maximises the user-friendliness of the interface. The flexibility to
support different sensors and magnets makes the system versatile and
opens the possibility for use in different applications. A low-cost
magnetic field sensors interface will therefore not only be economically
attractive, but also facilitate the integration of magnetic field
sensors in different contexts. In addition, the low-cost sensor
interface will serve as a development platform for the data evaluation
\gls{mrp} library and provide real measurement data from magnets. In
addition, the interface firmware creates a basis for the development of
a data protocol for exchanging measured values. This makes it easy to
integrate your own measuring devices into the \gls{mrp} ecosystem at a
later date. This is only possible with a minimal functional hardware and
firmware setup and was developed for this purpose first.

@@

The selection process for possible magnetic field sensors initially
focussed on the most common and cost-effective ones, especially those
that are already used in smartphones and are therefore widely available.
A key aspect of this selection was the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout.
The integration of integrated temperature sensors represents a
significant enhancement that will later enable precise temperature
compensation.

The use of analog sensors was purposefully avoided, though they are
suitable for more precise measurements and extended measuring ranges.
They were excluded because they require more carefully designed circuits
and more complicated energy management. In the context of the desired
goal of developing a cost-efficient and universally expandable Hall
sensor interface, the decision in favour of digital sensors seems
appropriate.

@@

The microcontroller firmware is software that is executed on a
microcontroller in an embedded system. It controls the hardware and
enables the execution of predefined functions. The firmware is used to
process input data, control output devices and performs specific tasks
according to the program code. It handles communication with sensors,
actuators and other peripheral devices, processing data and making
decisions. Firmware is critical to the functioning of devices.

@@

The flow chart
\ref{Unified_sensor_firmware_simplified_program_strucutre.png} shows the
start process and the subsequent main loop for processing the user
commands and sensor results. When the microcontroller is started, the
software checks whether known sensors are connected to \gls{i2c} or
\gls{uart} interfaces. If any are found (using a dedicated \gls{lut}
with sensor address translation information), the appropriate class
instances are created and these can later be used to read out
measurement results.

The next initialisation system is dedicated for multi-sensor
synchronisation \ref{sensor-syncronisation-interface}. The last step in
the setup is to configure communication with the host or connected
\gls{pc}. All implemented microcontroller platforms used (Raspberry Pi
Pico, STM32F4) have a \gls{usb} slave port. The used usb descriptor is a
\gls{usb} \gls{cdc}. This is used to emulate a virtual RS232
communication port using a \gls{usb} port on a \gls{pc} and usually no
additional driver is needed on modern host systems.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \passthrough{\lstinline!register irq on sync pin!} is
overwritten. To set one \passthrough{\lstinline!primary!} and several
\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to
\passthrough{\lstinline!secondary!} mode and synchronise the
measurements based on each sync pulse received. Since the presumed
\passthrough{\lstinline!primary!} sensor cannot register its own sync
pulse (because the pin is switched to output), there is a timeout branch
condition \passthrough{\lstinline!got pulse within 1000ms!} and this
becomes the \passthrough{\lstinline!primary!} sensor. This means that in
a chain of sensors there is exactly one
\passthrough{\lstinline!primary!} and many
\passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
this automatically jumps to \passthrough{\lstinline!primary!} sensor
operation through the
\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
synchronisation status can be queried via the user interface
\ref{communication-interface} using the \passthrough{\lstinline!opmode!}
\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
implementation here was that there is no numbering or sequence of the
individual sensors. This means that for the subsequent readout of the
measurements, it is only important that they are taken at the same
interval across all sensors. The sensor differentiation takes place
later in the \gls{mrp} \ref{software-readout-framework}-library by using
the sensor \gls{uuid}.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated
\passthrough{\lstinline!Voltcraft GM-70!} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of \passthrough{\lstinline!0-3T!} with
a resolution of \passthrough{\lstinline!0.1mT!}. It offers an
\passthrough{\lstinline!RS232!} interface with a documented protocol
\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.
This connectivity makes it possible to make the device compatible with
the Unified Sensor ecosystem using a separate interface software
\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
it does not offer the range of functions that the Unified Sensor
firmware offers.

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical \passthrough{\lstinline!RS232!} interface. As with the
other sensors, this interface consists of your
\passthrough{\lstinline!RaspberryPi Pico!} with an additional level
shifter. The Teslameter is connected to the microcontroller using two
free \gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol from
table \ref{Voltcraft_GM70_serial_protocol.csv} of the sensor was
implemented in a customized version of the
\passthrough{\lstinline!CustomSensor!} class
\ref{lst:CustomSensorClass}.

@@

User interaction points represent the core concept of the developed
library and are intended to provide user-friendliness on the one hand
and the rapid development of own analysis and optimization algorithms on
the other. For this purpose, the library was divided into individual
modules, which are shown in the graphic
\ref{MRP_library_module_high_level_overview.png}. In combination, these
represent a typical measurement-analysis-evaluation workflow of data.
For this purpose, a module system with standardised functional patterns
and data types was developed and packed together in a extendable Python
library.

@@

After these customization steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly. This also fulfills the goal of
making individual user-created algorithms interchangeable. If the user
now wishes to use a different \gls{cad} algorithm instead of the
\passthrough{\lstinline!HalbachMRIDesigner!}
\cite{HalbachMRIDesigner}, the other steps can simply be preserved
and only the new step needs to be implemented.

@@

Within the realm of measurement data, a diverse range of data points can
be seamlessly incorporated. The process is initiated by employing
specialized functions designed for the creation and addition of data
records. To configure parameters, ensuring a tailored approach to the
entire measurement process, these parameters act as a crucial bridge
between user preferences and the robust capabilities of the
\passthrough{\lstinline!MRPReading!} module.

@@

To enhance the accessibility and interpretability of the recorded data,
a dedicated module, \passthrough{\lstinline!MRPMagnetTypes!}, comes into
play. This module is specifically designed for the storage of physical
parameters pertaining to the magnets targeted for measurement. By
centralizing this information, users can streamline the subsequent
phases of evaluation and analysis, simplifying the overall process and
ensuring a more efficient and insightful exploration of the collected
data.

@@

An important aspect is data import and export. On the one hand, this
allows the library to reuse and archive the measurements. On the other
hand, the focus during development was that it is also possible to use
the data in other programs. For this purpose, an open, documented export
format must be selected. Ideally, this should be human-readable and
viewable with a simple text editor. This eliminates all binary-based
formats such as the Python pickle built into Python.

@@

The following code snippet \ref{lst:json_export_format_example} shows
the \gls{json} structure which is generated when a measurement thatt
using the library is exported. Here you can see that by using the
\gls{json} format, all measurement points and metadata are available in
readable plain text. This means that they can also be read out in other
programs. Using serialization, the \passthrough{\lstinline!MRPReading!}
class inherited from Python-\passthrough{\lstinline!Object!} class is
serialized via an dictionary conversion step. This \gls{json} string can
then be processed directly or written to the file system as a file.

@@

At the current described scenarios, it is only possible to detect and
use sensors that are directly connected to the host \gls{pc}. It has the
disadvantage that there must always be a physical connection. This can
make it difficult to install multiple sensors in measurement setups
where space or cable routing options are limited. So multibe sensor can
be connected to any \gls{pc} which is available on the network. This can
be a \gls{sbc} (e.g.~a Raspberry Pi). The small footprint and low power
consumption make it a good choice. It can also be used in a temperature
chamber.

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock as described in \ref{sensor-syncronisation-interface}.
this no longer works for long distances and the syncronisation must be
made via a shared network connection.

@@

The \passthrough{\lstinline!MRPReading!} is the key module of the
\gls{mrp} core. It is used to manage the measurement data and can be
imported and exported. The following example
\ref{lst:mrpexample_reading} shows how a measurement is created and
measurement points are added in the form of
\passthrough{\lstinline!MRPReadingEntry!} instances. An important point
is the management of the meta data, which further describes the
measurement. This is realised in the example using the
\passthrough{\lstinline!set\_additional\_data!} function.

@@

If no hardware sensor is available or for the generation of test data,
the \passthrough{\lstinline!MRPSimulation!} module is available. This
contains a series of functions that simulate various magnets and their
fields. The result is a complete \passthrough{\lstinline!MRPReading!}
measurement with a wide range of set meta data. The example
\ref{lst:mrpexample_simulation} illustrated the basic usage. Different
variations of the \passthrough{\lstinline!generate\_reading!} function
offers the user additional parameterisation options, such as random
polarisation direction or a defined centre-of-gravity vector. The data
is generated in the background using the
\passthrough{\lstinline!magpylib!} \cite{ortner2020magpylib} library
according to the specified parameters.

@@

Once data can be acquired using hardware or software sensors, the next
step is to analyse this data. \gls{mrp} provides some simple analysis
functions for this purpose. The code example shows the basic use of the
module. The \textbf{Evaluation} \ref{evaluation} chapter shows how the
user can implement their own algorithms and add them to the library.

@@

Eight random measurements are generated here. It is important that the
magnet type (here \passthrough{\lstinline!N45\_CUBIC\_15x15x15!}) is
specified. This is necessary so that the correct magnet cutouts can be
generated when creating the 3D model. After the measurements have been
generated, they are provided with a position and rotation offset
according to the Hallbach design and calucation scheme
\cite{HallbachMagnetDesignPaper} using the
\passthrough{\lstinline!MRPHallbachArrayGenerator!} module.

@@

Usability improvements in software libraries are crucial for efficient
and user-friendly development. Intuitive API documentation, clearly
structured code examples and improved error messages promote a smooth
developer experience. A \gls{gui} or \gls{cli} application for complex
libraries can make it easier to use, especially for developers with less
experience. Continuous feedback through automated tests and
comprehensive error logs enable faster bug fixing. The integration of
user feedback and regular updates promotes the adaptability of the
\gls{mrp}-library. Effective usability improvements help to speed up
development processes and increase the satisfaction of the developer
community. In the following, some of these have been added in and around
the \gls{mrp}-library, but they are only optional components for the
intended use.

@@

In the first version of the \gls{mrp}-library, the user had to write his
own Python scripts even for short measurement and visualisation tasks.
However, this was already time-consuming for reading out a sensor and
configuring the measurement parameters and metadata and quickly required
more than 100 lines of new Python code. Although such examples are
provided in the documentation, it must be possible for programming
beginners in particular to use them. To simplify these tasks, a
\gls{cli} \ref{example_measurement_analysis_pipeline.png} was
implemented. The libaray \gls{cli} implements the following
functionalities:

@@

After it is easy for users to carry out measurements using the
\gls{cli}, the next logical step is to analyse the recorded data. This
can involve one or several hundred data records. Again, the procedure
for the user is to write their own evaluation scripts using the
\gls{mrp}-library. This is particularly useful for complex analyses or
custom algorithms, but not necessarily for simple standard tasks such as
bias compensation or graphical plot outputs.

@@

In order to implement such a pipeline, the
\passthrough{\lstinline!yaml!} file format was chosen for the definition
of the pipeline, as this is for non programmers to understand and can
also be easily edited with a plain text editor. Detailed examples can be
found in the documentation
\cite{MagneticReadoutProcessingReadTheDocs}. The pipeline definition
consists of sections which execute the appropriate Python commands in
the background. The signatures in the \passthrough{\lstinline!yaml!}
file are called using \passthrough{\lstinline!reflection!} and a
real-time search of the loaded \passthrough{\lstinline!global()!}
functions symbol table \cite{PythonGlobalSymbolTable}. This system
makes almost all Python functions available to the user. To simplify
use, a pre-defined list of verified functions for use in pipelines is
listed in the documentation
\cite{MagneticReadoutProcessingReadTheDocs}. The following pipeline
definition \ref{lst:mrpuddp_example_yaml} shows the previously defined
steps \ref{example_measurement_analysis_pipeline.png} as
\passthrough{\lstinline!yaml!} syntax.

@@

Each pipeline step is divided into \passthrough{\lstinline!stages!},
which contain a name, the function to be executed and its parameters.
The various steps are then linked by using the
\passthrough{\lstinline!stage <name>!} makro as input parameter of the
next function to be executed (see comments in
\ref{lst:mrpuddp_example_yaml}). It is therefore also possible to use
the results of one function in several others without them directly
following each other. The disadvantages of this system are the
following:

@@

Software tests in libraries offer numerous advantages for improving
quality and efficiency. Firstly, they enable the identification of
errors and vulnerabilities before software is published as a new
version. This significantly improves the reliability of
\gls{mrp}-library applications. Tests also ensures consistent and
reliable performance, which is particularly important when libraries are
used by different users and for different usecases.

@@

For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor was
used for the evaulation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random
\passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used
here. These were placed in modified 3D printed holders
\ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
numbered. This allows them to be matched to the measurement results
later.

@@

The next step for the user is the implementation of the filter algorithm
\ref{lst:custom_find_similar_values_algorithm}. This can have any
function signature and is implemented in the file
\passthrough{\lstinline!UDPPFunctionCollection.py!}. This Python file is
loaded when the pipeline is started and all functions that are imported
here as a module or implemented directly can be called via the pipeline.
As this is a short algorithm, it was inserted directly into the file.
The parameter \passthrough{\lstinline!\_readings!} should later receive
the imported measurements from the
\passthrough{\lstinline!stage rawimport!}
\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
number of best measurements that are returned. The return parameter is a
list of measurements and should contain the measurements that are
closest to the mean value of all measurements after the function has
been executed.

@@

The hardware is based on widely used magnetic field sensors and low-cost
microcontrollers, which enables an easily expandable and applicable
solution for measuring magnets with repeatable accuracy. A particular
focus was placed on expandability by the user. Interchangeable modules
allow the user to develop their own analysis algorithms without having
to redesign everything from scratch.

>>>>

The following section defines some usecases that the future project
should be able to cover. These illustrate practical situations to
understand the functionality and added value of the implemented solution
for the user.

These were defined in the course of project planning and provide an
overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{evaluation}, the defined usecases are also used as a
reference to demonstrate the implemented capabilities of the solution.

@@

A defined main objective of this project is the development of a
cost-effective magnetic field sensors interface that is also universally
expandable. The focus is on mapping different sensors and being
compatible with different magnet types and shapes.

This ensures broad applicability in different scenarios. Another goal is
reproducibility to ensure consistent results. Easy communication with
standard PC hardware maximises the user-friendliness of the interface.

The flexibility to support different sensors and magnets makes the
system versatile and opens the possibility for use in different
applications. A low-cost magnetic field sensors interface will therefore
not only be economically attractive, but also facilitate the integration
of magnetic field sensors in different contexts.

In addition, the low-cost sensor interface will serve as a development
platform for the data evaluation \gls{mrp} library and provide real
measurement data from magnets. In addition, the interface firmware
creates a basis for the development of a data protocol for exchanging
measured values.

This makes it easy to integrate your own measuring devices into the
\gls{mrp} ecosystem at a later date. This is only possible with a
minimal functional hardware and firmware setup and was developed for
this purpose first.

@@

The selection process for possible magnetic field sensors initially
focussed on the most common and cost-effective ones, especially those
that are already used in smartphones and are therefore widely available.

A key aspect of this selection was the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout.
The integration of integrated temperature sensors represents a
significant enhancement that will later enable precise temperature
compensation.

The use of analog sensors was purposefully avoided, though they are
suitable for more precise measurements and extended measuring ranges.
They were excluded because they require more carefully designed circuits
and more complicated energy management.

In the context of the desired goal of developing a cost-efficient and
universally expandable Hall sensor interface, the decision in favour of
digital sensors seems appropriate.

@@

The microcontroller firmware is software that is executed on a
microcontroller in an embedded system. It controls the hardware and
enables the execution of predefined functions. The firmware is used to
process input data, control output devices and performs specific tasks
according to the program code.

It handles communication with sensors, actuators and other peripheral
devices, processing data and making decisions. Firmware is critical to
the functioning of devices.

@@

The flow chart
\ref{Unified_sensor_firmware_simplified_program_strucutre.png} shows the
start process and the subsequent main loop for processing the user
commands and sensor results. When the microcontroller is started, the
software checks whether known sensors are connected to \gls{i2c} or
\gls{uart} interfaces.

If any are found (using a dedicated \gls{lut} with sensor address
translation information), the appropriate class instances are created
and these can later be used to read out measurement results.

The next initialisation system is dedicated for multi-sensor
synchronisation \ref{sensor-syncronisation-interface}. The last step in
the setup is to configure communication with the host or connected
\gls{pc}. All implemented microcontroller platforms used (Raspberry Pi
Pico, STM32F4) have a \gls{usb} slave port.

The used usb descriptor is a \gls{usb} \gls{cdc}. This is used to
emulate a virtual RS232 communication port using a \gls{usb} port on a
\gls{pc} and usually no additional driver is needed on modern host
systems.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \passthrough{\lstinline!register irq on sync pin!} is
overwritten. To set one \passthrough{\lstinline!primary!} and several
\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to
\passthrough{\lstinline!secondary!} mode and synchronise the
measurements based on each sync pulse received.

Since the presumed \passthrough{\lstinline!primary!} sensor cannot
register its own sync pulse (because the pin is switched to output),
there is a timeout branch condition
\passthrough{\lstinline!got pulse within 1000ms!} and this becomes the
\passthrough{\lstinline!primary!} sensor. This means that in a chain of
sensors there is exactly one \passthrough{\lstinline!primary!} and many
\passthrough{\lstinline!secondary!} sensors.

In single-sensor operation, this automatically jumps to
\passthrough{\lstinline!primary!} sensor operation through the
\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
synchronisation status can be queried via the user interface
\ref{communication-interface} using the \passthrough{\lstinline!opmode!}
\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
implementation here was that there is no numbering or sequence of the
individual sensors.

This means that for the subsequent readout of the measurements, it is
only important that they are taken at the same interval across all
sensors. The sensor differentiation takes place later in the \gls{mrp}
\ref{software-readout-framework}-library by using the sensor \gls{uuid}.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated
\passthrough{\lstinline!Voltcraft GM-70!} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of \passthrough{\lstinline!0-3T!} with
a resolution of \passthrough{\lstinline!0.1mT!}. It offers an
\passthrough{\lstinline!RS232!} interface with a documented protocol
\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.

This connectivity makes it possible to make the device compatible with
the Unified Sensor ecosystem using a separate interface software
\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
it does not offer the range of functions that the Unified Sensor
firmware offers.

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical \passthrough{\lstinline!RS232!} interface. As with the
other sensors, this interface consists of your
\passthrough{\lstinline!RaspberryPi Pico!} with an additional level
shifter.

The Teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol from
table \ref{Voltcraft_GM70_serial_protocol.csv} of the sensor was
implemented in a customized version of the
\passthrough{\lstinline!CustomSensor!} class
\ref{lst:CustomSensorClass}.

@@

User interaction points represent the core concept of the developed
library and are intended to provide user-friendliness on the one hand
and the rapid development of own analysis and optimization algorithms on
the other.

For this purpose, the library was divided into individual modules, which
are shown in the graphic
\ref{MRP_library_module_high_level_overview.png}. In combination, these
represent a typical measurement-analysis-evaluation workflow of data.
For this purpose, a module system with standardised functional patterns
and data types was developed and packed together in a extendable Python
library.

@@

After these customization steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly.

This also fulfills the goal of making individual user-created algorithms
interchangeable. If the user now wishes to use a different \gls{cad}
algorithm instead of the \passthrough{\lstinline!HalbachMRIDesigner!}
\cite{HalbachMRIDesigner}, the other steps can simply be preserved
and only the new step needs to be implemented.

@@

Within the realm of measurement data, a diverse range of data points can
be seamlessly incorporated. The process is initiated by employing
specialized functions designed for the creation and addition of data
records.

To configure parameters, ensuring a tailored approach to the entire
measurement process, these parameters act as a crucial bridge between
user preferences and the robust capabilities of the
\passthrough{\lstinline!MRPReading!} module.

@@

To enhance the accessibility and interpretability of the recorded data,
a dedicated module, \passthrough{\lstinline!MRPMagnetTypes!}, comes into
play. This module is specifically designed for the storage of physical
parameters pertaining to the magnets targeted for measurement.

By centralizing this information, users can streamline the subsequent
phases of evaluation and analysis, simplifying the overall process and
ensuring a more efficient and insightful exploration of the collected
data.

@@

An important aspect is data import and export. On the one hand, this
allows the library to reuse and archive the measurements. On the other
hand, the focus during development was that it is also possible to use
the data in other programs.

For this purpose, an open, documented export format must be selected.
Ideally, this should be human-readable and viewable with a simple text
editor. This eliminates all binary-based formats such as the Python
pickle built into Python.

@@

The following code snippet \ref{lst:json_export_format_example} shows
the \gls{json} structure which is generated when a measurement thatt
using the library is exported. Here you can see that by using the
\gls{json} format, all measurement points and metadata are available in
readable plain text.

This means that they can also be read out in other programs. Using
serialization, the \passthrough{\lstinline!MRPReading!} class inherited
from Python-\passthrough{\lstinline!Object!} class is serialized via an
dictionary conversion step. This \gls{json} string can then be processed
directly or written to the file system as a file.

@@

At the current described scenarios, it is only possible to detect and
use sensors that are directly connected to the host \gls{pc}. It has the
disadvantage that there must always be a physical connection. This can
make it difficult to install multiple sensors in measurement setups
where space or cable routing options are limited.

Multibe sensor can be connected to any \gls{pc} which is available on
the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
footprint and low power consumption make it a good choice. It can also
be used in a temperature chamber.

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface.

If several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock as described in \ref{sensor-syncronisation-interface}.
this no longer works for long distances and the syncronisation must be
made via a shared network connection.

@@

The \passthrough{\lstinline!MRPReading!} is the key module of the
\gls{mrp} core. It is used to manage the measurement data and can be
imported and exported. The following example
\ref{lst:mrpexample_reading} shows how a measurement is created and
measurement points are added in the form of
\passthrough{\lstinline!MRPReadingEntry!} instances.

An important point is the management of the meta data, which further
describes the measurement. This is realised in the example using the
\passthrough{\lstinline!set\_additional\_data!} function.

@@

If no hardware sensor is available or for the generation of test data,
the \passthrough{\lstinline!MRPSimulation!} module is available. This
contains a series of functions that simulate various magnets and their
fields. The result is a complete \passthrough{\lstinline!MRPReading!}
measurement with a wide range of set meta data.

The example \ref{lst:mrpexample_simulation} illustrated the basic usage.
Different variations of the \passthrough{\lstinline!generate\_reading!}
function offers the user additional parameterisation options, such as
random polarisation direction or a defined centre-of-gravity vector. The
data is generated in the background using the
\passthrough{\lstinline!magpylib!} \cite{ortner2020magpylib} library
according to the specified parameters.

@@

Once data can be acquired using hardware or software sensors, the next
step is to analyse this data. \gls{mrp} provides some simple analysis
functions for this purpose. The code example shows the basic use of the
module. The \passthrough{\lstinline!Evaluation!} \ref{evaluation}
chapter shows how the user can implement their own algorithms and add
them to the library.

@@

Eight random measurements are generated here. It is important that the
magnet type (here \passthrough{\lstinline!N45\_CUBIC\_15x15x15!}) is
specified. This is necessary so that the correct magnet cutouts can be
generated when creating the 3D model.

After the measurements have been generated, they are provided with a
position and rotation offset according to the Hallbach design and
calucation scheme \cite{HallbachMagnetDesignPaper} using the
\passthrough{\lstinline!MRPHallbachArrayGenerator!} module.

@@

Usability improvements in software libraries are crucial for efficient
and user-friendly development. Intuitive API documentation, clearly
structured code examples and improved error messages promote a smooth
developer experience. A \gls{gui} or \gls{cli} application for complex
libraries can make it easier to use, especially for developers with less
experience. Continuous feedback through automated tests and
comprehensive error logs enable faster bug fixing.

The integration of user feedback and regular updates promotes the
adaptability of the \gls{mrp}-library. Effective usability improvements
help to speed up development processes and increase the satisfaction of
the developer community. In the following, some of these have been added
in and around the \gls{mrp}-library, but they are only optional
components for the intended use.

@@

In the first version of the \gls{mrp}-library, the user had to write his
own Python scripts even for short measurement and visualisation tasks.
However, this was already time-consuming for reading out a sensor and
configuring the measurement parameters and metadata and quickly required
more than 100 lines of new Python code.

Although such examples are provided in the documentation, it must be
possible for programming beginners in particular to use them. To
simplify these tasks, a \gls{cli}
\ref{example_measurement_analysis_pipeline.png} was implemented. The
libaray \gls{cli} implements the following functionalities:

@@

After it is easy for users to carry out measurements using the
\gls{cli}, the next logical step is to analyse the recorded data. This
can involve one or several hundred data records. Again, the procedure
for the user is to write their own evaluation scripts using the
\gls{mrp}-library.

This is particularly useful for complex analyses or custom algorithms,
but not necessarily for simple standard tasks such as bias compensation
or graphical plot outputs.

@@

In order to implement such a pipeline, the
\passthrough{\lstinline!yaml!} file format was chosen for the definition
of the pipeline, as this is for non programmers to understand and can
also be easily edited with a plain text editor. Detailed examples can be
found in the documentation
\cite{MagneticReadoutProcessingReadTheDocs}. The pipeline definition
consists of sections which execute the appropriate Python commands in
the background.

The signatures in the \passthrough{\lstinline!yaml!} file are called
using \passthrough{\lstinline!reflection!} and a real-time search of the
loaded \passthrough{\lstinline!global()!} functions symbol table
\cite{PythonGlobalSymbolTable}. This system makes almost all Python
functions available to the user. To simplify use, a pre-defined list of
verified functions for use in pipelines is listed in the documentation
\cite{MagneticReadoutProcessingReadTheDocs}. The following pipeline
definition \ref{lst:mrpuddp_example_yaml} shows the previously defined
steps \ref{example_measurement_analysis_pipeline.png} as
\passthrough{\lstinline!yaml!} syntax.

@@

Each pipeline step is divided into \passthrough{\lstinline!stages!},
which contain a name, the function to be executed and its parameters.
The various steps are then linked by using the
\passthrough{\lstinline!stage <name>!} makro as input parameter of the
next function to be executed (see comments in
\ref{lst:mrpuddp_example_yaml}).

It is therefore also possible to use the results of one function in
several others without them directly following each other. The
disadvantages of this system are the following:

@@

Software tests in libraries offer numerous advantages for improving
quality and efficiency. Firstly, they enable the identification of
errors and vulnerabilities before software is published as a new
version.

This significantly improves the reliability of \gls{mrp}-library
applications. Tests also ensures consistent and reliable performance,
which is particularly important when libraries are used by different
users and for different usecases.

@@

For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor was
used for the evaulation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random
\passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used
here.

These were placed in modified 3D printed holders
\ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
numbered. This allows them to be matched to the measurement results
later.

@@

The next step for the user is the implementation of the filter algorithm
\ref{lst:custom_find_similar_values_algorithm}. This can have any
function signature and is implemented in the file
\passthrough{\lstinline!UDPPFunctionCollection.py!}. This Python file is
loaded when the pipeline is started and all functions that are imported
here as a module or implemented directly can be called via the pipeline.
As this is a short algorithm, it was inserted directly into the file.

The parameter \passthrough{\lstinline!\_readings!} should later receive
the imported measurements from the
\passthrough{\lstinline!stage rawimport!}
\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
number of best measurements that are returned. The return parameter is a
list of measurements and should contain the measurements that are
closest to the mean value of all measurements after the function has
been executed.

@@

The hardware is based on widely used magnetic field sensors and low-cost
microcontrollers, which enables an easily expandable and applicable
solution for measuring magnets with repeatable accuracy.

A particular focus was placed on expandability by the user.
Interchangeable modules allow the user to develop their own analysis
algorithms without having to redesign everything from scratch.
